
\documentclass[11pt]{article}
\usepackage{natbib}


\title{permuter: An R Package for Randomization Inference}
\author{K. Ottoboni$^{1,*}$, J. Millman$^{2}$ and P.B. Stark$^1$}
\begin{document}

% Produce the title
\maketitle
% Brief abstract of the paper
\abstract{
Software packages for randomization inference are few and far between.
This forces researchers either to rely on specialized stand-alone programs or to use classical statistical tests that may require implausible assumptions about their data-generating process.
The absence of a flexible and comprehensive package for randomization inference is an obstacle for researchers from a wide range of disciplines who turn to R as a language for carrying out their data analysis.
We present \texttt{permuter}, a package for randomization inference.
We illustrate the program's capabilities with several examples:
\begin{itemize}
\item a randomized experiment comparing the student evaluations of teaching for male and female instructors \citep{macnell:article}
\item a study of the association between salt consumption and mortality at the level of nations
\item an assessment of inter-rater reliability for a series of labels assigned by multiple raters to video footage of children on the autism spectrum
\end{itemize}

We discuss future plans for \texttt{permuter} and the role of software development in Statistics.
}


\thispagestyle{empty}

% References, if any. Remove this if there are no references.
\bibliographystyle{apalike}
\begin{thebibliography}{99}

\bibitem[\protect\astroncite{MacNell et al.}{2014}]{macnell:article} MacNell, L. and Driscoll, A. and Hunt, A. N. (2014). What's in a Name: Exposing Gender Bias in Student Ratings of Teaching. \textit{Innovative Higher Education}, %\textbf{}, 
1--13.


\end{thebibliography}

\end{document}

